Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-17 paper.qmd
Updated Figure 2 projection

axes_obj <- gen_axes(  
  proj = projection * 5,
  limits = 0.12,
  axis_pos_x = -0.1,
  axis_pos_y = -0.1,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0.01)

two_curvy_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#2b8cbe") +
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.125, 0.075)) + 
  ylim(c(-0.125, 0.075)) +
  interior_annotation("b", c(0.08, 0.93), cex = 2) +
  theme(
    legend.position = "none"
  )
```

>>>>

axes_obj <- gen_axes(  
  proj = projection * 6,
  limits = 0.13,
  axis_pos_x = -0.1,
  axis_pos_y = -0.1,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0.0113)

two_curvy_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#2b8cbe") +
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.125, 0.13)) + 
  ylim(c(-0.125, 0.13)) +
  interior_annotation("b", c(0.08, 0.93), cex = 2) +
  theme(
    legend.position = "none"
  )
```
